\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg)
library(rsvg)
r_refs("r-references.bib")
```

---
nocite: |
  `r cite_r("r-references.bib")`
---

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Introduction

@@

```{r flowchart }
Flowchart1 <- grViz("digraph nicegraph{

@@

## Procedure
Our study had four objectives. First, to develop an instrument to assess individual's light exposure behavior . Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure. Third to gather structural validity evidence for the latent structure obtained in EFA.
[@furrPsychometricsIntroduction2014]. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

@@

# Results
```{r Normality assumption EFA}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
#KMO test
KMO <- KMO(LB)

@@

as.data.frame(upper)
min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
max.cor <- abs(max(upper)) # max. correlation coefficent of the matrix

@@

```{r figCor,fig.cap= "Iter-correlation of the items",results='asis'}

@@

>>>>

```{r setup, include = FALSE}
library(papaja) # devtools::install_github("crsh/papaja")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(MOTE)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
r_refs("references.bib")
```

---
nocite: |
  `r cite_r("references.bib")`
---

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r setup-chunk, include=FALSE}
knitr::opts_chunk$set(dev = "png",
                      dpi = 300,
                      echo = FALSE,
                      cache = TRUE)
```

# Introduction

@@

```{r flowchart, include=FALSE}
Flowchart1 <- grViz("digraph nicegraph{

@@

## Procedure
Our study had four objectives. First, to develop an instrument to assess individual's light exposure behavior . Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure. Third to gather structural validity evidence for the latent structure obtained in EFA [@furrPsychometricsIntroduction2014]. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

@@

# Results
```{r Normality assumption EFA, include=FALSE}
LB <- read_excel("recoded not reversed_EFA.xlsx")
LB$X1 <- NULL
#KMO test
KMO <- KMO(LB)

@@

min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
max.cor <- abs(max(upper)) # max. correlation coefficent of the matrix

@@

```{r figCor,out.width="50%",fig.cap= "Iter-correlation of the items",results='asis'}

@@

```{r factor_identification, eval=FALSE, include=FALSE}

#correlations <- polychoric(LB.factor, correct = 0)

# Parallel analysis
 paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
      status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
      color=TRUE, col=c("black","red","blue"),
      lty=c(1,2,3), lwd=1, legend=TRUE, file="parallel.png",
      width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)

# HULL
hullEFA(LB,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
        details = TRUE)

Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model. In our data set parallel analysis with 500 iterations indicated six-factor solution. However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.

```{r fac.id, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
knitr::include_graphics('parallel.png')
scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)
knitr::include_graphics('HUll method.png')
